PubCrawl: A Paper Search Engine

### 2012-05-15 report/paper.tex
Add abstract

\title{PubCrawl: A Paper Search Engine}
\author{Frank Li \\
Abhishek Sarkar \\
Manasi Vartak}
\date{May 16, 2012}

@@

@@

	To address this issue, we designed PubCrawl, a paper search engine. Using this system allows researchers to query for the most important and relevant papers in a field, particularly one they are not familiar with. PubCrawl uses Apache Lucene for text indexing to measure a paper’s relevance to a query, and an adaptation of PageRank on the papers citation graph for weighting a paper’s importance. Currently all papers in the Association of Computing Machinery (ACM) Digital Library database have been processed. A simple web user interface is provided, where users can input queries and weights for what attributes they feel is most important, to tune the result rankings to fit what they feel is most appropriate. The top papers are returned, with hyperlinks to the papers’ ACM homepage.

@@

There are a few paper search engines currently in existence: CiteseerX, Google Scholar, and Microsoft Academic Search.

CiteseerX's data set is scraped from the web by a crawler, and processed in an automated fashion. This has provided CiteseerX with wide and largely hands-off coverage of papers. However, due to the purely automated approach used and the heterogeneity in data representation on the web, the data collected contains errors and missing information. For example, the crawler has mistaken the wrong string for the title of a number of papers.

@@

PubCrawl is designed to rank papers based on relevance and importance. To measure relevance, we use Apache Lucene, a high-performance text search engine library for Java. Lucene is used to provide text indexing, returning the papers most textually relevant to a query. To measure importance, we use a variation of the classic PageRank algorithm on the citation graph of papers. The weighting between the text indexing and PageRank score is an input the users can provide, as discussed in \ref{sec:implementation}. Currently, the ACM dataset has been gathered and applied using PubCrawl.

@@

Components in the citation graph are the other source of complication. Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain. The ACM data exhibits a large number (???? exact number????) of components, with a small number of large components and a large number of components with just a few papers (Figure ???). Small components are papers that don't cite any other papers in the data set and aren't heavily cited. This implies that nodes in small components should not be highly ranked. 
To adjust for this, nodes are categorized into the components they belong in. Instead of initializing node scores to be a constant value such as 1, they are instead initialized to a score linear to the size of the component containing the nodes. Intuitively, this means that papers in larger components will receive higher scores, as desired.

@@

\begin{itemize}
\item For the score source $E$, we use a uniform value. We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score.

>>>>

\title{PubCrawl: A Paper Search Engine}
\author{Frank Li (frankli@mit.edu) \\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}
\date{May 16, 2012}

@@

\begin{abstract}
Searching for documents ranked by relevance is a well-studied problem for web
pages. In particular, there are frameworks for estimating relevance as a
function of the content of the document and algorithms for estimating relevance
as a function of incoming links. However, further specialization of these
techniques is required to search a corpus of academic papers. Academic papers
are highly structured, lending additional weight to matches which appear in
important sections such as the title or abstract. Moreover, citations have
contextual information which changes the weight which should be contributed to
cited papers. Here we describe PubCrawl, a search engine built for the ACM
Digital Library. The system allows users to weight the relative importance of
matches in the title, abstract, full text, and the PageRank of each hit,
providing a platform to test further refinements of the algorithms. We evaluate
the system in user studies.
\end{abstract}

@@

	To address this issue, researchers have create paper search engines, such as Google Scholar and CiteseerX. However, the ranking process for these systems is largely privately maintained. In this paper, we investigate the process of ranking in the academic papers setting. An understanding of this is important to create a better search system.

	To do this, we designed PubCrawl, a paper search engine, as a testing bed for ranking mechanisms. In building PubCrawl, we used Apache Lucene for text indexing to measure a paper’s relevance to a query, and an adaptation of PageRank on the papers citation graph for weighting a paper’s importance. Currently all papers in the Association of Computing Machinery (ACM) Digital Library database have been processed. A simple web user interface is provided, where users can input queries and weights for what attributes they feel is most important, to tune the result rankings to fit what they feel is most appropriate. The top papers are returned, with hyperlinks to the papers’ ACM homepage.

@@

There are a few paper search engines currently in existence, such as CiteseerX and Google Scholar. Their ranking process is largely maintained privately, but several characteristics of both are described in this section.

CiteseerX's data set is scraped from the web by a crawler, and processed in an automated fashion. This has provided CiteseerX with wide and largely hands-off coverage of papers. However, due to the purely automated approach used and the heterogeneity in data representation on the web, the data collected contains errors and missing information. For example, the crawler has mistaken the wrong string for the title of a number of papers. This leads to some errors in the processing of both the paper data and queries.

Google Scholar also operates with a crawler, and exhibits some of the same dirty data issues as CiteseerX. Additionally, Google Scholar has been shown to be heavily influenced by citation count, which may be inappropriate for some user queries.

@@

PubCrawl is designed to rank papers based on relevance and importance. To measure relevance, we use Apache Lucene, a high-performance text search engine library for Java. Lucene is used to provide text indexing, returning the papers most textually relevant to a query. To measure importance, we use a variation of the classic PageRank algorithm on the citation graph of papers. The weighting between the text indexing and PageRank score is an input the users can provide, as discussed in \ref{sec:implementation}. Currently, the ACM dataset has been gathered and applied using PubCrawl. Through the design of the system, we discuss the effect of a number of its features.

@@

\begin{figure}[t]
\centering
	\includegraphics[width=5in]{images/component-graph}
	\caption{Sizes of components in the ACM data set and the number of each size's occurrence.}	
	\label{comp-size}
\end{figure}

Components in the citation graph are the other source of complication. Papers in the same component are either both part of the same citation chain or share a common ancestor or descendant in their respective chain. The ACM data exhibits 45,571 total components, with one large component of 176,285 papers, and a large number of smaller components ranging in size from one to ten papers, as displayed in Figure \ref{comp-size}. Small components are papers that don't cite many or any other papers in the data set and aren't heavily cited. This implies that nodes in small components should not be highly ranked.

To adjust for this, nodes are categorized into the components they belong in. Instead of initializing node scores to be a constant value such as 1, they are instead initialized to a score linear to the size of the component containing the nodes. Intuitively, this means that papers in larger components will receive higher scores, as desired.

@@

\begin{itemize}
\item For the score source $E$, we use a uniform value. We minimize the value of $E$ that still results in convergence, to reduce the total amount of freely created score. In our system, we found $E=0.1$ to be appropriate.
